Concurrent Programming with CXL

### 2020-06-24 book/paper.tex
Made pass over non-blocking synch

\chapter{The CXL Virtual Machine}
\label{ch:cxlmachine}
\index{CXL virtual machine}

@@

@@

\section*{Exercises}
\begin{problems}
\item A \emph{seqlock} consists of a lock and a version number.
An update operation acquires the lock, increments the version number, makes the
changes to the data structure, and then releases the lock.  A read-only operation
does not use the lock.  Instead, it retrieves the version number,
reads the data structure, and then checks if the
version number has not changed.  If it has, read-only operation is retried.
Use a seqlock to implement a bank much like Exercise~\ref{ex:bank}, with
one seqlock for the entire bank (i.e., no locks on individual accounts).
Method \texttt{transfer} is an update operation; method \texttt{total} is a
read-only operation.  Explain how a \texttt{seqlock} can lead to starvation.
\end{problems}

>>>>

\chapter{The CXL Virtual Machine}
\label{ch:cxlmachine}
\index{CXL Virtual Machine}

@@

Determining if an implementation of a concurrent data structure
is linearizable involves finding what are known as the
\emph{linearization points}
\index{linearization point}
of the operations in an execution.  These are the unique
points in time at which an operation appears to execute atomically.
The linearization points for the \texttt{lst\_insert} and
\texttt{lst\_remove} operations coincide exactly with the update
of the \texttt{before.next} pointer.
The linearization point of a \texttt{lst\_contains} method
execution depends on whether the value is found or not.
If found, it coincides with retrieving the pointer to the node
that has the value.
If not found, it coincides with retrieving the pointer to the
\texttt{inf} node.

@@

\section*{Exercises}
\begin{problems}
\item Add read-only methods to the data structure in Figures~\ref{fig:lst1}
and~\ref{fig:lst2} that report the size of the list, the minimum value in the
list, the maximum value in the list, and the sum of the values in the list.
Are they linearizable?  If so, what are their linearization points?
\item A \emph{seqlock} consists of a lock and a version number.
An update operation acquires the lock, increments the version number, makes the
changes to the data structure, and then releases the lock.  A read-only operation
does not use the lock.  Instead, it retrieves the version number,
reads the data structure, and then checks if the
version number has not changed.  If it has, read-only operation is retried.
Use a seqlock to implement a bank much like Exercise~\ref{ex:bank}, with
one seqlock for the entire bank (i.e., no locks on individual accounts).
Method \texttt{transfer} is an update operation; method \texttt{total} is a
read-only operation.  Explain how a \texttt{seqlock} can lead to starvation.
\end{problems}
